A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-06 manuscript.Rmd
better explain where software is installed

The file `.repro/Dockerfile_manual` is by default empty and is supposed to allow dependencies outside of R, like system libraries or external software.
The most convinient way to install software on Ubuntu is through its package manager `apt`.
This snipped installs python:

>>>>

The file `.repro/Dockerfile_manual` is by default empty and is supposed to allow dependencies outside of R, like system libraries or external software.
Remember, the software environment of the Docker image is completely separate from software installed on your computer.
This separation is excellent for reproducibility, but requires you to install software on an operating system that may not be familiar to you.
The images supplied by [@boettigerIntroductionRockerDocker2017] are based on Ubuntu, and hence software has to be installed in a way that is compatible with Ubuntu.
The most convenient way to install software on Ubuntu is through its package manager `apt`.
This snipped installs python, added to `.repro/Dockerfile_manual` you get an image that has python available:
